### 2019-01-11 fe_px_paper/fe_body_text.tex
Merged in Amanda's early edits

The next generation of nuclear medicine would appear to be based upon the production of novel, emerging radionuclides \cite{Qaim201731}. 
The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  makes possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives \cite{Mulford2005,Muller2014}.
While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production. 
% 
% 
% 
% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue \cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose \cite{Muller2014,Bentzen2005,Srivastava2012}. 
% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.  
% Change up the next sentance a bit
% Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
% \cite{Qaim201731}. 
% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
One particular group of  emerging radionuclides are the various positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications \cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET \cite{Graves2016}. 
As part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
This was carried out in a  thin-foil stacked-target experiment, using proton irradiation of natural iron foils with titanium and copper monitor foils.
While recent work has been performed in the 40--100\,MeV energy region, this work seeks to complement these measurements and extend them down to reaction thresholds, to investigate the feasibility of production using the international network   of low-energy medical cyclotrons   \cite{Graves2016}.

Manganese radionuclides are desirable for radiopharmaceutical applications, as manganese is a chemically versatile element, biologically relevant, and essential in trace quantities. 
Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH \cite{Graves2015}.
\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection \cite{Dong2015}.
Its lifetime allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}. 
\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging \cite{Graves2015}. 
However, its  long lifetime and unfavorable decay gamma-rays (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) make it undesirable for clinical applications, but easily shipped worldwide and highly suitable for pre-clinical imaging \cite{Dong2015}.
The \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min, $I_{\beta^+}$ = 96.6\%, $E_{\beta\text{, avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose  \cite{Dong2015}.
Another emerging manganese radionuclide is \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), whose short lifetime makes it clinically suited for rapid metabolic studies \cite{Wang2017}.
\ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
In addition, \ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging applications \cite{Wang2017}.

@@

While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio \cite{Dong2015,Wang2017}.
Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region \cite{PhysRevC.73.034613,PhysRevC.45.1171}.
These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in \textred{f$_{7/2}$} subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve the predictive capabilities of  reaction modeling codes. 
In addition, these experiments provide valuable insight into the challenges  involved in precision cross section data measurements.

@@

The work described herein follows the  methods utilized in our recent work and established by Graves \etal\ 
% for the measurement of cross sections in stacked target irradiations   
for monitor reaction characterization of beam energy and fluence in stacked target irradiations \cite{Voyles2018a,Graves2016}.
% 
% Make sure to add this back in for the journal article
% 
% 
Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here  \cite{springer2017investigation}.

@@

A pair of target stacks were constructed for this work, due to the large energy range desired to be spanned.
One stack covers the 55--20\,MeV range and the other covers 25--0\,MeV, to minimize the systematic uncertainties associated with significant degradation of beam energy.
In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  
% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation \cite{Cumming1963}. 
% For targets, a
A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
In each stack, seven foils of each metal were cut down to 2.5$\times$2.5\,cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
% , along with the propagated uncertainty in areal density.
% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
Targets of 6061 aluminum alloy  serve as proton energy degraders  between energy positions.
% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy, and mounts on the end of an electrically-isolated beamline.
The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table}.

@@

% \caption{Specifications of the  target stack design in the present work. The proton beam enters the stack upstream of the 249.8 \mmicro m SS profile monitor, and is transported through the stack in the order presented here. The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$. Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\ \cite{Graves2016}. At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}

@@

\caption{Specifications of the 25\,MeV and 55\,MeV target stack designs in the present work. The proton beam enters the stack upstream of the SS-5 and SS-3 profile monitors, respectively, and is transported through the stack in the order presented here. The 6061 aluminum degraders have a measured density of approximately 2.69 g/cm$^3$. Their areal densities were determined using the variance minimization techniques described  in this work  and our earlier paper \cite{Voyles2018a}. 
% the earlier paper by Graves \etal\ \cite{Graves2016}.

@@

% For consistency, a
A single detector was used in this measurement, an ORTEC GMX Series (model \#GMX-50220-S)  High-Purity Germanium (HPGe) detector.
The detector is a nitrogen-cooled coaxial n-type HPGe with a 0.5\,mm beryllium window, and a 64.9\,mm diameter, 57.8\,mm long crystal.
Samples were counted at fixed positions ranging 5--60  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy and efficiency for each position.
The foils were counted  for a period of 4 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities.
An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec_femn}.
% An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code FitzPeaks \cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma ray spectra \cite{Aarnio2001}.
% , which has been shown to perform best in comparisons with other common analysis codes \cite{Jackman2014}.
%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.

@@

% Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
The net  counts in each fitted gamma-ray photopeak were converted into  activities for the decaying  activation products, using calibrated detector efficiencies and gamma-ray intensities for each transition.
% and  corrections for gamma-ray attenuation within each foil packet
% The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.  
% 
% Re-introduce this next line for the journal version
% 
% 
% The nuclear decay data used in this work is tabulated, for reference, in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of Appendix \ref{sec:fe_data}.
The   lifetimes and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
\cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database  \cite{berger2011xcom}.
% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
% Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
% activity for each gamma-ray possesses a 
The total propagated uncertainty in  activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.

As in our previous work, these activities used to calculate cross sections, and are differentiated between cumulative and independent \cite{Voyles2018a}.
For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus. 
% In addition, 
Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.  
Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, so that  independent cross sections may be reported \cite{bateman1910solution,Cetnar2006}.

>>>>

The next generation of nuclear medicine would appear to be based upon the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  makes possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives\,\cite{Mulford2005,Muller2014}.
While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production. 
% 
% 
% 
% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue\,\cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose\,\cite{Muller2014,Bentzen2005,Srivastava2012}. 
% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.  
% Change up the next sentance a bit
% Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
%\,\cite{Qaim201731}. 
% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
One particular group of  emerging radionuclides are the various positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}. 
As part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
This was carried out in a  thin-foil stacked-target experiment, using proton irradiation of natural iron foils with titanium and copper monitor foils.
While recent work has been performed in the 40--100\,MeV energy region, this work seeks to complement these measurements and extend them down to reaction thresholds, to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}.

Manganese radionuclides are desirable for radiopharmaceutical applications, as manganese is a chemically versatile element that is biologically relevant and essential in trace quantities. 
Manganese possesses well-established biochemistry, and has been proven to be chelated well by DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection\,\cite{Dong2015}.
Its lifetime allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}. 
\ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
However, its  long lifetime and unfavorable decay gamma-rays (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) make it undesirable for clinical applications, but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
The \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min, $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
Another emerging manganese radionuclide is \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 97.09\%, $E_{\beta\text{, avg}}$ = 0.973\,MeV), whose short lifetime makes it clinically suited for rapid metabolic studies\,\cite{Wang2017}.
\ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
In addition, \ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging applications\,\cite{Wang2017}.

@@

While these efforts have been motivated by the production cross section of the \ce{^{51,52g,52m}Mn} radionuclides for PET studies, this experiment offers an opportunity to study the distribution of angular momentum in compound nuclear and direct pre-equilibrium reactions via observation of the \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$\pm$0.2\,min; J$^\pi=2^+$) to \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d; J$^\pi=6^+$)   ratio\,\cite{Dong2015,Wang2017}.
Measurements of isomer-to-ground state ratios have been used for over 20\,years to probe the spin distribution of excited nuclear states in the A\,$\approx$\,190 region\,\cite{PhysRevC.73.034613,PhysRevC.45.1171}.
These measurements provide a range of cross section data invaluable to not only the medical isotope production community, but  also serve to measure the spin distribution in \textred{f$_{7/2}$} subshell nuclei via the observation of isomer-to-ground state ratios, and  as new data to improve the predictive capabilities of  reaction modeling codes. 
In addition, these experiments provide valuable insight into the challenges  involved in precision cross section data measurements.

@@

The work described herein follows the  methods utilized in our recent work and established by Graves \etal\ 
% for the measurement of cross sections in stacked target irradiations   
for monitor reaction characterization of beam energy and fluence in stacked target irradiations\,\cite{Voyles2018a,Graves2016}.
% 
% Make sure to add this back in for the journal article
% 
% 
Preliminary analysis  was previously reported in the Master's thesis of one co-author, but the conclusive results of this work are described here\,\cite{springer2017investigation}.

@@

A pair of target stacks were constructed for this work, due to the large energy range desired to be spanned.
One stack covers the 55--20\,MeV range and the other covers 25--0\,MeV, to minimize the systematic uncertainties associated with significant degradation of beam energy.
In addition, the complementary  energy  of the  stacks helps build confidence  through multiple overlapping measurements between 20--25\,MeV.  
% A stacked-target design was utilized for this work in order that the (p,x) cross sections for each reaction channel could be measured at multiple energy positions in a single irradiation\,\cite{Cumming1963}. 
% For targets, a
A series of nominal 25\,\mmicro m \ce{^{nat}Fe} foils (99.5\%, lot \#LS470411), 25\,\mmicro m \ce{^{nat}Ti} foils (99.6\%, lot \#LS471698), and 25\,\mmicro m \ce{^{nat}Cu} foils (99.95\%, lot \#LS471698) were used (all from Goodfellow Corporation, Coraopolis, PA 15108, USA) as targets.
In each stack, seven foils of each metal were cut down to 2.5$\times$2.5\,cm squares and characterized --- for each foil, length and width measurements were taken at four different locations using a digital caliper (Mitutoyo America Corp.), thickness measurements were taken at four different locations using a digital micrometer (Mitutoyo America Corp.), and four mass measurements were taken using an analytical balance after cleaning the foils with isopropyl alcohol.
Using these length, width, and mass readings, the areal density and its uncertainty (in mg/cm$^2$) for each foil was calculated.
% , along with the propagated uncertainty in areal density.
% The foils were tightly sealed into \enquote{packets} using two pieces of  3M 1205-Series Kapton polyimide film tape --- each piece of tape consists of 38.1 \mmicro m of an acrylic adhesive (nominal 4.49 mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61 mg/cm$^2$).
The foils were tightly sealed into \enquote{packets} using two pieces of  3M 5413-Series Kapton polyimide film tape --- each piece of tape consists of 43.2 \mmicro m of a silicone adhesive (nominal 4.79\,mg/cm$^2$) on 25.4 \mmicro m of a polyimide backing (nominal 3.61\,mg/cm$^2$).
The sealed foils were mounted over the hollow center of  1.5875 mm-thick aluminum frames.
Targets of 6061 aluminum alloy  serve as proton energy degraders  between energy positions.
% One \ce{^{nat}Fe}, one \ce{^{nat}Cu}, and one \ce{^{nat}Ti} mounted foil were bundled together using baling wire for each energy position.
The target box, seen in \autoref{fig:fe_target_stack}, is machined from 6061 aluminum alloy, and mounts on the end of an electrically-isolated beamline.
The specifications of both target stack designs for this work are presented in \autoref{tab:fe_stack_table}.

@@

% \caption{Specifications of the  target stack design in the present work. The proton beam enters the stack upstream of the 249.8 \mmicro m SS profile monitor, and is transported through the stack in the order presented here. The 6061 aluminum degraders have a measured density of approximately 2.80 g/cm$^3$. Their areal densities were determined using the variance minimization techniques described  in this work  and the earlier paper by Graves \etal\\,\cite{Graves2016}. At both the front and rear of the target stack's foils, a 316 stainless steel foil is inserted to serve as a beam profile monitor --- after end-of-bombardment (EoB), decay radiation emitted from these activated stainless steel foils were used to develop radiochromic film (Gafchromic EBT3), revealing the spatial profile of the beam entering and exiting the stack.}

@@

\caption{Specifications of the 25\,MeV and 55\,MeV target stack designs in the present work. The proton beam enters the stack upstream of the SS-5 and SS-3 profile monitors, respectively, and is transported through the stack in the order presented here. The 6061 aluminum degraders have a measured density of approximately 2.69 g/cm$^3$. Their areal densities were determined using the variance minimization techniques described  in this work  and an earlier paper\,\cite{Voyles2018a}. 
% the earlier paper by Graves \etal\\,\cite{Graves2016}.

@@

% For consistency, a
A single detector was used in this measurement, an ORTEC GMX Series (model \#GMX-50220-S)  High-Purity Germanium (HPGe) detector.
The detector is a nitrogen-cooled coaxial n-type HPGe with a 0.5\,mm beryllium window, and a 64.9\,mm diameter, 57.8\,mm long crystal.
Samples were counted at fixed positions ranging 5--60  cm (5\% maximum permissible dead-time) from the front face of the detector, with a series of standard calibration sources used to determine energy and efficiency for each position.
The foils were counted  for a period of 4 weeks following end-of-bombardment (EoB), to accurately quantify all induced activities.
An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec_femn}.
% An example of one of the gamma-ray spectra collected in such a fashion is shown in \autoref{fig:gspec}.
For all spectra collected, net peak areas were fitted using the gamma spectrometry analysis code FitzPeaks\,\cite{fitzgerald2009fitzpeaks}, which utilizes the SAMPO fitting algorithms for gamma-ray spectra\,\cite{Aarnio2001}.
% , which has been shown to perform best in comparisons with other common analysis codes\,\cite{Jackman2014}.
%, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.

@@

% Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
The net  counts in each fitted gamma-ray photopeak were converted into  activities for the decaying  activation products, using calibrated detector efficiencies and gamma-ray intensities for each transition.
% and  corrections for gamma-ray attenuation within each foil packet
% The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.  
% 
% Re-introduce this next line for the journal version
% 
% 
% The nuclear decay data used in this work is tabulated, for reference, in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of Appendix \ref{sec:fe_data}.
The   lifetimes and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
\cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database\,\cite{berger2011xcom}.
% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
% Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
% activity for each gamma-ray possesses a 
The total propagated uncertainty in  activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.

As in our previous work, these activities are used to calculate cross sections, and are differentiated between cumulative and independent\,\cite{Voyles2018a}.
For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus. 
% In addition, 
Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.  
Solutions to the first- and higher-order  Bateman equations are used for separation of  feeding contributions from decay precursors, so that  independent cross sections may be reported\,\cite{bateman1910solution,Cetnar2006}.

% Since many of the reaction products populated by energetic protons are more than one decay off of stability, many of these are produced not only  directly by reactions, but also indirectly by decay down a mass chain.
% To this end, it is useful to differentiate between the types of cross sections reported in this work. 
% For the first observable product nuclei in a mass chain, its (p,x) cross section will be reported as a cumulative cross section ($\sigma_c$), which is the sum of direct production of that nucleus, as well as decay of its  precursors and any other independent cross sections leading to that nucleus. 
% % In addition, 
% Cumulative cross sections will be reported whenever it is impossible to use decay spectrometry to distinguish independent production of a nucleus from decay feeding.
% For all remaining observed reaction products in the mass chain, and cases where no decay precursors exist, independent cross sections ($\sigma_i$) will be reported, allowing for determination of the independent production via subtraction  and facilitating comparison to reaction model calculations.  
% 
% 
% 
% % To convert these activities into cross sections, c
% Corrections must be made for the decay of the various reaction products during the time between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB, from the measured activities.
% The use of  multiple gamma-rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma-ray observation.
% For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
% % \begin{equation}
% % A\pp{t} = A_0 e^{-\lambda t}
% % \end{equation}
% Nonlinear regression was used for this fitting process, minimizing on $\chi^2$\,/\,degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ could be reported as as well.
% As with the gamma-ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of \ref{sec:fe_data}.
% In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{t=0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation\,\cite{bateman1910solution,Cetnar2006}:
% \begin{equation}
% A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_{i,0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
% \end{equation}
% where $j$ refers to a precursor nucleus populating a specific end-product.  
% While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
% \begin{equation}
% A_2\pp{t} = \dfrac{A_{1,0}\lambda_2}{\lambda_1 - \lambda_2} \pp{e^{-\lambda_2 t} - e^{-\lambda_1 t}} + A_{2,0} e^{-\lambda_2 t}
% \end{equation}
% In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, so that the feeding contributions from decay could be separated and an independent cross section reported.
% After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.
